---
title: "Workshop_Material"
output: ioslides_presentation
date: "2023-10-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Installing packages and getting started
```{r, echo = TRUE, comment = '#'}
#install.packages("gt")

library(gt)
library(tidyverse)

pizza_place_raw<- pizzaplace

head(pizza_place_raw)
```

## The Top 10 Best Selling Pizzas
We want to get the best selling pizzas from this list. Also include the type.
How would you go about it?
```{r, echo = TRUE}
top_10_pizzas <- pizza_place_raw %>% 
  group_by(name, type) %>% 
  count(name) %>% 
  arrange(desc(n)) %>% 
  head(10)
```
## Using gt to Get the Table Presentation Ready
Now, using gt, give this table a titel:
Also using gt, how would you change the pizza names, wrighting out all the names without abriviations (classic_dlx = classic deluxe). 
```{r, echo = TRUE}
top_10_pizzas %>% 
  gt() %>% 
  tab_header("Top Ten Best Selling Pizzas") %>% 
  sub_values(values = "classic_dlx", replacement = "Classic Deluxe") #%>% 
  #sub_values(values = "bbq_ckn", replacement = "BBQ Chicken")

```